Impact of the 2016 Presidential Election on Urban Mobility: Who is Affected the Most?

### 2019-12-06 manuscript.Rmd
averaged travel times

```{r}
week_1 <- travel_time_sf %>% filter(year == 2016, month == 9, week == 1)
```

>>>>

```{r}
travel_time_sf$NumRoads <- sapply(st_intersects(travel_time_sf,dc_roads),length)
travel_time_sf$NumMetro <- sapply(st_intersects(travel_time_sf,metro_line),length)

#Averaged travel times over weeks 1 and 2 in January
weeks12 <- travel_time_sf %>% 
  filter(year %in% 2017) %>% 
  filter(month %in% 1) %>% 
  filter(week %in% 1:2) %>%
  select(GEOID,mean_travel_time) %>%
  as.data.frame() %>%
  group_by(GEOID) %>%
  summarize(MeanTimeNorm = mean(mean_travel_time))

weeks34 <- travel_time_sf %>% 
  filter(year %in% 2017) %>% 
  filter(month %in% 1) %>% 
  filter(week %in% 3:4) %>%
  select(GEOID,mean_travel_time) %>%
  as.data.frame() %>%
  group_by(GEOID) %>%
  summarize(MeanTimeIng = mean(mean_travel_time))

mod1data <- travel_time_sf %>%
  dplyr::select(GEOID, starts_with('med_'),starts_with('white'),starts_with('asian'),starts_with('black'),starts_with('car_trans'),starts_with('public_trans'),NumRoads,NumMetro) %>%
  left_join(weeks12)

mod2data <- travel_time_sf %>%
  dplyr::select(GEOID, starts_with('med_'),starts_with('white'),starts_with('asian'),starts_with('black'),starts_with('car_trans'),starts_with('public_trans'),NumRoads,NumMetro) %>%
  left_join(weeks34)

weeksdiff = left_join(weeks12,weeks34) %>%
  mutate(diffMeanTime = MeanTimeIng-MeanTimeNorm)

mod3data <- travel_time_sf %>%
  dplyr::select(GEOID, starts_with('med_'),starts_with('white'),starts_with('asian'),starts_with('black'),starts_with('car_trans'),starts_with('public_trans'),NumRoads,NumMetro) %>%
  left_join(weeksdiff)
```
